Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-05-21 manuscript.Rmd
adjusted some chunk option

```{r pca_acet_sel echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "PCA all cores, only samples present in both acet and SPT"}
pca_acet_select[1]
```

>>>>

```{r pca_acet_sel, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "PCA all cores, only samples present in both acet and SPT"}
pca_acet_select[1]
```
